Comparing human and model-based forecasts of COVID-19 in Germany and Poland

### 2021-10-14 analysis/analysis.Rmd
clean code and files

  # delete and rename a few columns
  del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                          !(grepl("interval", names(df)))]
  del_cols <- c(del_cols, "coverage_deviation")
  df[, (del_cols) := NULL] 
  setnames(df, old = c("interval_score_sd, sharpness"), 
           new = c("WIS - sd", "dispersion"))

@@

# create tables

# regular models
filtered_data[model %in% regular_models] %>%
  make_table()

>>>>

  # delete and rename a few columns
  setnames(df, 
           old = c("interval_score_sd", "sharpness"), 
           new = c("WIS - sd", "dispersion"))
  del_cols <- names(df)[(grepl("_sd", names(df)) | grepl("0.5", names(df))) &
                          !(grepl("interval", names(df)))]
  del_cols <- c(del_cols, "coverage_deviation")
  df[, (del_cols) := NULL]

@@

# create tables
# regular models
filtered_data[model %in% regular_models] %>%
  make_table()

### 2021-10-14 manuscript/manuscript.Rmd
clean code and files

Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application  (https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information available until Monday. The application was built using the shiny and golem R packages [@golem; @shiny] and is available in the `crowdforecastr` R package [@crowdforecastr]. To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values. The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e. as `sd(c(log(value4) - log(value3), log(value3) - log(value2), ...))`[a]). 
Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  [@COVID19DataExplorer]. These data included e.g. notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.

@@

$GP_t$ is an approximate Hilbert space Gaussian process as defined in [@approxGP] using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20% of the number of days used in fitting). The length scale of the Gaussian process[b] was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days. The magnitude of the Gaussian process was assumed to be normally distributed centred at 0 with a standard deviation of 0.1.

@@

```{r performance-locations, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-4.png")
```

@@

[a]-> maths?
[b]that sentence seems odd. Is it supposed to be that way @Sam.Abbott@lshtm.ac.uk

>>>>

Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application  (https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information available until Monday. The application was built using the shiny and golem R packages [@golem; @shiny] and is available in the `crowdforecastr` R package [@crowdforecastr]. To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values. The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e. as `sd(c(log(value4) - log(value3), log(value3) - log(value2), ...))`). 
Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  [@COVID19DataExplorer]. These data included e.g. notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.

@@

$GP_t$ is an approximate Hilbert space Gaussian process as defined in [@approxGP] using a Matern 3/2 kernel using a boundary factor of 1.5 and 17 basis functions (20% of the number of days used in fitting). The length scale of the Gaussian process was given a log-normal prior with a mean of 21 days, and a standard deviation of 7 days truncated to be greater than 3 days and less than 60 days. The magnitude of the Gaussian process was assumed to be normally distributed centred at 0 with a standard deviation of 0.1.

@@

```{r performance-locations, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-2-weeks-locations-all-v4.png")
```

@@
